---
title: "**Homework assignment title.**"
date: "Last compiled on: `r format(Sys.time(), '%d/%m/%Y, %H:%M:%S')`."
authors:
  - name: Paco de Lucía
    address: 778899
  - name: Baby Yoda
    address: 774455
  - name: Chick Corea
    address: 884422
  - name: An alternative for big teams - Chick Corea (884422), Baby Yoda (774455), Paco de Lucía (778899), Suzanne Ciani (365411), Alan Turing (312511) and others. 
abstract: |
  Summary of main findings and conclusions. Optional section.
keywords:
  - Optional section. quantitative finance
  - financial risk
  - financial modeling in R
  - Optional section.
fontsize: 12pt
urlcolor: blue
spacing: halfline
bibliography: mybibfile.bib
output: rticles::oup_article
link-citations: yes
citation_package: natbib
---

```{=tex}
\hypersetup{linkcolor=blue}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # By default, show code; set to FALSE to hide it
knitr::opts_chunk$set(fig.pos = 'H') # Places figures on pages separate from text
knitr::opts_chunk$set(out.width = '100%', dpi=300) # Figure resolution and size
knitr::opts_chunk$set(fig.env = "figure") # Latex figure environment
```

# Introduction.

*Look how you can add web links in the following sentence*. This template is based on the generic OUP template available [here](https://academic.oup.com/icesjms/pages/General_Instructions). **Now, look how you can add a different font**. This is useful for \texttt{file} or \texttt{function names}. The original OUP sample tex document, providing more details on preferred formatting for LaTeX documents, is included with the template in the file `ouparticle_sample.tex`.

Here are some sample references. *Reference in brackets as in a list.* Please see [@Hull; @carhart1997persistence] for a full discussion of multi-factor models. Bibliography will appear at the end of the document. *Second, without brackets, separated by a comma.* See @Hull, @Hull2, @cochrane2009asset for a formal demonstration of analytical results, and [@carhart1997persistence; @cochrane1996cross] for some empirical results.

# Methodology.

An equation with a label for cross-referencing:

```{=tex}
\begin{equation}\label{eq:eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]
\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0
(\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}
```
This equation can be referenced as follows: Eq. \ref{eq:eq1}. Now a simpler equation:

```{=tex}
\begin{equation}\label{eq:eq2}
w=\sum^{20}_{i=1}[1/n^i]
\end{equation}
```

This equation can be referenced as Eq. \ref{eq:eq2}.

We can also write equations within the main text as here: $w=\sum^{20}_{i=1}[1/n^i]$.
\

**PMF group 3:00pm.** Assume $n=0.9$, plot the values of $w$ (y-axis) as a function of $i$ (x-axis). Add your name as the plot title. Report your code in a code chunk below. Hint: you need to use the `cumsum()` function.


## A subsection.

A numbered list:

1)  First numbered point

2)  Second numbered point

    -   Subpoint

A bullet list:

-   First point
-   Second point

# Results.

## Generate a figure.

```{r fig1, fig.cap = "This is the first figure.", echo = TRUE}
plot(1:10, main = "Some data", xlab = "Distance (cm)", 
     ylab = "Time (hours)")
```

You can reference this figure as follows: Fig. \ref{fig:fig1}.

```{r fig2, fig.cap="This is the second figure.",echo=TRUE}
plot(1:5, pch = 19, main = "Some data", xlab = "Distance (cm)", 
     ylab = "Time (hours)")
```

Reference to second figure: Fig. \ref{fig:fig2}

## Generate a table using `xtable`.

```{r tab1, results="asis", echo=TRUE}
df = data.frame(ID = 1:3, code = letters[1:3])

# Creates tables that follow OUP guidelines using xtable
library(xtable) 
print(xtable(df, caption = "This is the table caption", 
             label = "tab:tab1"), comment = FALSE)
```

You can reference this table as follows: Table \ref{tab:tab1}.

## Generate a table using `kable`.

```{r anothertable, echo=TRUE}
df = data.frame(ID = 1:3, code = letters[1:3])

# kable can alse be used for creating tables
knitr::kable(df, caption = "This is the table caption", format = "latex",
             booktabs = TRUE, label = "tab2")
```

You can reference this table as follows: Table \ref{tab:tab2}.

# Nombres de los alumnos de PMF (fall 2021).

## Grupo 3:00pm.

Diana Jacquelinne Soto Alcaraz Hola a todos, que tengan buen inicio de semestre

Juan Pablo Almada Burr- Saludos a todos.

Bernardo Amador Padilla - Hola, saludos.

Christian Contreras Hernández - S.O.S.

Melanie Flores García - Hola Grupo

Luis Fernando Rodríguez Parra HOla, saludos a todos

Diego Valdés Contreras - Hola:)

María Fernanda Rendón Muro

Eugenio Murillo Nader - Hola grupo! 

Adriana Beatriz Santos Monterroza

Oscar David Cortés Gutiérrez - Hola, excelente semestre!

Pompilio Rainiero Amador Sandoval

José Gonzalo Morones Intriago-Saludos!

Andrea Newell Jasso

María Julia Romero Rico - Holaa!!

Claudia Michelle de los Ríos Arellano

Salvador Adrián Sánchez Macías - hola a todos

Enrique Gallegos Pateiro

César Alejandro Marroquín Garibay- hola todos.

Natalia Azcárraga Kuri - llevo demasiados intentos, y no puedoooooo

Cecilia Reyes Villarreal

Ricardo Díaz Ceballos Corral- Saludos! suerte!

Medardo Chávez Aguilar - Hola a todos!

Sofía Aitana Salcedo Martínez

Karina Albarrán Herrera - Hola a todos, buen inicio de semestre.

César Jacob Linares Murguia

Edgar Fernández Reynaga - Hola a todos. 

Marianne Obele Coll

Emilio Noriega González - Saludos a todo el grupo....

Allan Alvarado Lozano - Saludos desde Guadalajara 

Lara Hanna Weitgasser - Hola a todos y todas!


## Grupo 6:00pm.

Juan Andrés Castro Moreno

Manuel Alejandro Manríquez Quezada

Juan Carlos Bocanegra Rivera

Alejandro Adolfo Pastor Lara- Saludos a todo el grupo!

Adalberto Vladimir Palomares Ramos

Diana Angélica Sandoval Ramírez - hola! saludos a todos

Luis Daniel Puente Flores - Saludos a todos, buen inicio de semestre

José Ramón Santos Buhl

Raúl Antonio Valdez Lozano

Jesús Oscar López Mendoza

Eduardo Cuesy Saldaña

Héctor Alejandro Faz Zepeda

Adriana Sofía Salcido Berumen - ¡Saludos!

Luis Arturo Payán Quiñones

Daniela Pizano Chávez- Hola profe, saludos!!!

David Armando Placencia Aguilar

Marco Francisco Beltrán Soto - Hola profe, espero que haya tenido un muy buen fin, saludos!

Román Muñoz Loza Saludos desde Aguascalientes!

Oscar Ventura Montaño

Manuel Eduardo Romero Jara

Juan Francisco Marcial Posas - Hola a todos desde Orizaba

Jorge Andrés Ángeles Luévano - Saludos desde Chihuahua, Profesor!

Andrés Amílkar Yáñez Frías

Nicolai Reiners - listo (por fin)...

Félix Muñoz Rodríguez

David Villard Linares

Álvaro Rubio Pina

Eyleen Lizeth López Cueva-Saludos desde Perú


## Task.

Use R code to numerically demonstrate whether the following equation is true:

```{=tex}
\begin{equation}\label{eq:eq3}
ln(e)+(sin^2x+cos^2x) > \sum^{\infty}_{n=0}1/2^n
\end{equation}
```

Write your R code and results here, below the equation \ref{eq:eq3} and before the conclusion. Please include your name.

### Diana Jacquelinne Soto Alcaraz A00227348.

```{r}
x<-1
equation1<-log(exp(1))+((sin(x)^2)+(cos(x)^2))
equation1

n<- seq(0:50000)
equation2 <- sum(1/2^n)
equation2

equation1>equation2

```

### Juan Pablo Almada Burr A00227349.

```{r}
x<-1
eq<- log(exp(x))+(sin(x)^2)+(cos(x)^2) 
eq

n<- seq_len(1000)
eq3 <- sum(1/2^n)
eq3

is.it.true <- eq > eq3
if(is.it.true == TRUE) {print ("Equation is true!")}
if(is.it.true == FALSE) {print("Equation is false!")}
```

**PMF group 6:00pm.** Plot $y=log(x)$, where $x=0.1, 0.2, 0.3,...,5$. Add your name as the plot title. Report your code in a code chunk below.


# Conclusion.

You can cross-reference sections and subsections as follows: Section \ref{methodology.} and Section \ref{a-subsection.}.

***Note:*** the last section in the document will be used as the section title for the bibliography.

# References.

